On the treatment of discordant detrital zircon U--Pb data

### 2021-02-19 paper.tex
Accepted version.

\title{Redefining U--Pb discordance}

@@

\begin{figure}[t]
  \includegraphics[width=7.3cm]{TW-option-1234.pdf}
  \caption{Discordance cutoffs for four of the six discordance
    definitions discussed in Sections~\ref{sec:discordance1} and
    \ref{sec:discordance2}. The $d_{p}$ and $d_c$ criteria are not
    shown because they depend on the analytical uncertainty of the
    measurements, which may vary between studies. The grey envelopes
    mark cutoff values of $d_r=20\%$ (relative age filter),
    $d_t=300$~Ma (absolute age filter), $d_{sk}=2\%$ (Stacey--Kramers
    filter) and $d_{a}=15\%$ (perpendicular Aitchison distance) on a
    Tera-Wasserburg concordia diagram, which is plotted in logarithmic
    space to provide a more balanced view of the old and young ends of
    the time scale. The $d_{sk}$ and $d_t$ envelopes are truncated
    where they cross over into physically impossible negative isotope
    ratio space.}
  \label{fig:agediscordance}
\end{figure}

@@

\bibliographystyle{copernicus}
\bibliography{/home/pvermees/Dropbox/biblio.bib}

>>>>

\title{On the treatment of discordant detrital zircon U--Pb data}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{TW-option-1234.pdf}
  \caption{Discordance cutoffs for four of the six discordance
    definitions discussed in Sections~\ref{sec:discordance1} and
    \ref{sec:discordance2}. The $d_{p}$ and $d_c$ criteria are not
    shown because they depend on the analytical uncertainty of the
    measurements, which may vary between studies. The grey envelopes
    mark cutoff values of $d_r=20\%$ (relative age filter),
    $d_t=300$~Ma (absolute age filter), $d_{sk}=2\%$ (Stacey--Kramers
    filter) and $d_{a}=15\%$ (perpendicular Aitchison distance) on a
    Tera-Wasserburg concordia diagram, which is plotted in logarithmic
    space to provide a more balanced view of the old and young ends of
    the time scale. The $d_{sk}$ and $d_t$ envelopes are truncated
    where they cross over into physically impossible negative isotope
    ratio space.}
  \label{fig:agediscordance}
\end{figure}

@@

%\bibliographystyle{copernicus}
%\bibliography{/home/pvermees/Dropbox/biblio.bib}

\begin{thebibliography}{14}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{{\tt #1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{https://doi.org/\discretionary{}{}{}#1}\else
  \providecommand{\doi}{https://doi.org/\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{Aitchison(1986)}]{aitchison1986}
Aitchison, J.: The statistical analysis of compositional data, London, Chapman
  and Hall, 1986.

\bibitem[{Cohen(1992)}]{cohen1992}
Cohen, J.: A power primer., Psychological bulletin, 112, 155, 1992.

\bibitem[{Gehrels(2011)}]{gehrels2011}
Gehrels, G.: {Detrital zircon U-Pb geochronology: Current methods and new
  opportunities}, in: Tectonics of sedimentary basins: Recent advances, edited
  by Busby, C. and Azor, A., chap.~2, pp. 45--62, Wiley Online Library, 2011.

\bibitem[{{Ludwig}(1998)}]{ludwig1998}
{Ludwig}, K.~R.: {On the treatment of concordant uranium-lead ages}, Geochimica
  et Cosmochimica Acta, 62, 665--676, \doi{10.1016/S0016-7037(98)00059-3},
  1998.

\bibitem[{{McIntyre} et~al.(1966){McIntyre}, {Brooks}, {Compston}, and
  {Turek}}]{mcintyre1966}
{McIntyre}, G.~A., {Brooks}, C., {Compston}, W., and {Turek}, A.: {The
  Statistical Assessment of Rb-Sr Isochrons}, Journal of Geophysical Research,
  71, 5459--5468, 1966.

\bibitem[{{Nemchin} and {Cawood}(2005)}]{nemchin2005}
{Nemchin}, A.~A. and {Cawood}, P.~A.: {Discordance of the U--Pb system in
  detrital zircons: Implication for provenance studies of sedimentary rocks},
  Sedimentary Geology, 182, 143--162, \doi{10.1016/j.sedgeo.2005.07.011}, 2005.

\bibitem[{Pawlowsky-Glahn et~al.(2015)Pawlowsky-Glahn, Egozcue, and
  Tolosana-Delgado}]{pawlowsky2015}
Pawlowsky-Glahn, V., Egozcue, J.~J., and Tolosana-Delgado, R.: Modeling and
  analysis of compositional data, John Wiley \& Sons, 2015.

\bibitem[{Puetz et~al.(2018)Puetz, Ganade, Zimmermann, and
  Borchardt}]{puetz2018}
Puetz, S.~J., Ganade, C.~E., Zimmermann, U., and Borchardt, G.: {Statistical
  analyses of global U-Pb database 2017}, Geoscience Frontiers, 9, 121--145,
  2018.

\bibitem[{Schoene(2014)}]{schoene2014}
Schoene, B.: U--Th--Pb Geochronology, Treatise on geochemistry, 4, 341--378,
  2014.

\bibitem[{Spencer et~al.(2016)Spencer, Kirkland, and Taylor}]{spencer2016}
Spencer, C.~J., Kirkland, C.~L., and Taylor, R.~J.: {Strategies towards
  statistically robust interpretations of in situ U--Pb zircon geochronology},
  Geoscience Frontiers, 7, 581--589, 2016.

\bibitem[{Stacey and Kramers(1975)}]{stacey1975}
Stacey, J. and Kramers, J.: Approximation of terrestrial lead isotope evolution
  by a two-stage model, Earth and Planetary Science Letters, 26, 207--221,
  1975.

\bibitem[{Vermeesch(2013)}]{vermeesch2013}
Vermeesch, P.: Multi-sample comparison of detrital age distributions, Chemical
  Geology, 341, 140--146, 2013.

\bibitem[{Vermeesch(2018)}]{vermeesch2018c}
Vermeesch, P.: {\texttt{IsoplotR}: a free and open toolbox for geochronology},
  Geoscience Frontiers, 9, 1479--1493, 2018.

\bibitem[{Zimmermann et~al.(2018)Zimmermann, Mark, Chew, and
  Voice}]{zimmermann2018}
Zimmermann, S., Mark, C., Chew, D., and Voice, P.~J.: {Maximising data and
  precision from detrital zircon U-Pb analysis by LA-ICPMS: The use of core-rim
  ages and the single-analysis concordia age}, Sedimentary geology, 375, 5--13,
  2018.

\end{thebibliography}
